---
title: "RWorksheet_Basa#4a"
author: "Jared J Basa"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
Table <- data.frame(
  Shoe_size = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0),
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)

print(Table)
```
a. Describe the data.
Data contains shoe size, height, and gender.

b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.
```{r}
male <- Table[Table$Gender == "M",]
female <- Table[Table$Gender == "F",]

print(male)
print(female)
```


c. Find the mean of shoe size and height of the respondents. Write the R scripts and its
result.
```{r}
meanShoe_size <- mean(Table$Shoe_size)
meanHeight <- mean(Table$Height)

print(paste("Mean Shoe Size:", meanShoe_size))
print(paste("Mean Height:", meanHeight))
```


d. Is there a relationship between shoe size and height? Why?
```{r}
plot(Table$Shoe_size, Table$Height, main="Shoe Size vs Height", xlab="Shoe Size", ylab="Height")
```

Factors
A nominal variable is a categorical variable without an implied order. This means
that it is impossible to say that ‘one is worth more than the other’. In contrast,
ordinal variables do have a natural ordering.
Example:
Gender <- c("M","F","F","M")
factor_Gender <- factor(Gender)
factor_Gender

## [1] M F F M
## Levels: F M

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
Consider data consisting of the names of months:
"March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August", "July","December","August","August","September","November","February",|
April")
```{r}
vectorMonths <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "November", "November", "February", "May", "August", "July", "December", "August", "August", "September", "November", "February", "April")


factor_months_vector <- factor(vectorMonths)
print(factor_months_vector)
```

3. Then check the summary() of the months_vector and factor_months_vector. | Interpret the results of both vectors. Are they both equally useful in this case? 
```{r}
summary_vectorMonths <- summary(vectorMonths)
summary_factor_months_vector <- summary(factor_months_vector)

print(summary_vectorMonths)
print(summary_factor_months_vector)
```

4. Create a vector and factor for the table below.
Direction Frequency
East 1
West 4
North 3
Note: Apply the factor function with required order of the level.
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```{r}
factor_data <- c("East", "West", "North")
frequency_vector <- c(1, 4, 3)
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```
5. Enter the data below in Excel with file name = import_march.csv

Figure 2: Excel Data

a. Import the excel file into the Environment Pane using read.table() function.
Write the code. 
```{r}
data <- read.table("import_march.csv", header = TRUE, sep = ",")
```
b. View the dataset. Write the R scripts and its result.
```{r}
data
```

