---
title: "RWorksheet_Basa#4a"
author: "Jared J Basa"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
Table <- data.frame(
  Shoe_size = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0),
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)

print(Table)
```
a. Describe the data.
Data contains shoe size, height, and gender.

b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.
```{r}
male <- Table[Table$Gender == "M",]
female <- Table[Table$Gender == "F",]

print(male)
print(female)
```


c. Find the mean of shoe size and height of the respondents. Write the R scripts and its
result.
```{r}
meanShoe_size <- mean(Table$Shoe_size)
meanHeight <- mean(Table$Height)

print(paste("Mean Shoe Size:", meanShoe_size))
print(paste("Mean Height:", meanHeight))
```


d. Is there a relationship between shoe size and height? Why?
```{r}

```

