---
title: "Untitled"
author: "Jared J Basa"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
---
title: "Untitled"
output: pdf_document
date: "2024-11-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(polite)
library(rvest)
library(dplyr)
library(stringr)
library(purrr)
library(ggplot2)

scrape_amazon_category <- function(url, n_products = 30)
{
  page <- read_html(url)
  
  product_names <- page %>%
    html_nodes(".s-title-instructions-style") %>%
    html_text(trim = TRUE)
  
  product_prices <- page %>%
    html_nodes(".a-price-whole") %>%
    html_text(trim = TRUE)
  
  product_ratings <- page %>%
    html_nodes(".a-icon-alt")%>%
    html_text(trim = TRUE)
  
  data <- tibble(
    Name = head(product_names, n_products),
    Price = head(product_prices, n_products),
    Rating = head(product_rating, n_products)
  )
  return(data)
}

category-urls <- c(
  "https://www.amazon.pl/s?k=luggages&__mk_pl_PL=%C3%85M%C3%85%C5%BD%C3%95%C3%91&crid=14BSP4WDDWZXA&sprefix=luggages%2Caps%2C311&ref=nb_sb_noss_2",
  "https://www.amazon.pl/s?k=power+bank&crid=192VQDAYY8QNL&sprefix=power%2Caps%2C311&ref=nb_sb_ss_ts-doa-p_1_5",
  "https://www.amazon.pl/s?k=mouse+pad&crid=2SAL73G0QO9WM&sprefix=mouse%2Caps%2C330&ref=nb_sb_ss_ts-doa-p_2_5",
  "https://www.amazon.pl/s?k=keyboard&crid=2I5SF3CY53BRY&sprefix=keybo%2Caps%2C295&ref=nb_sb_ss_ts-doa-p_1_3",
  "https://www.amazon.pl/s?k=bluetooth+speaker&crid=XJ3HRBWSZKKI&sprefix=bluet%2Caps%2C347&ref=nb_sb_ss_ts-doa-p_3_5"
)

category_data <- list
```


```

