---
title: "RWorksheet_Basa#1"
author: "Jared J Basa"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Vector: operator
a.
```{r}
seq_seq <- -5:5
print (seq_seq)
```
b. 
```{r}
x <- 1:7
print(x)
```
2. vector using seq()
```{r}
seq(1, 3, by=0.2)
print(seq)
```
3. A factory has a census of its workers. There are 50 workers in total. The following
list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,
18.

1

a. Access 3rd element, what is the value?
```{r}
mylist <- list(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
print(mylist[3])
```

b. Access 2nd and 4th element, what are the values?
```{r}
mylist <- list(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
print(mylist[c(2, 4)])
```

c. Access all but the 4th and 12th element is not
included. Write the R script and its output.
```{r}
mylist <- list(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
print(mylist[-c(4, 12)])
```
4. *Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the vector, names(x).
```{r}
names <- c("first"=3, "second"=0, "third"=9)
print(names)
```
a. Print the results. Then access x[c("first", "third")].
Describe the output.
```{r}
names <- c("first"=3, "second"=0, "third"=9)
names[c( 1, 3)]
```


b. Write the code and its output.
```{r}
names <- c("first"=3, "second"=0, "third"=9)
names[c( 1, 3)]
names
```
5. Create a sequence x from -3:2.
a. Modify 2nd element and change it to 0;
x[2] <- 0
x
```{r}
x <- -3:2
x[2] <- 0
x
```

Describe the output.

b. Write the code and its output.
```{r}
x <- -3:2
x[2] <- 0
x
```
[1] -3  0 -1  0  1  2
6. *The following data shows the diesel fuel purchased by Mr. Cruz.

2

Month Jan Feb March Apr May June
Price per liter (PhP) 52.50 57.25 60.00 65.00 74.25 54.00
Purchase–quantity(Liters) 25 30 40 50 10 45
a. Create a data frame for month, price per liter (php)
and purchase-quantity (liter). Write the R scripts and
its output.
```{r}
months <- c("Jan", "Feb", "March", "Apr", "May", "Jun")
php <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
liters <- c(25, 30, 40, 50, 10, 45)
df <- data.frame(months, php, liters)
df
```

b. What is the average fuel expenditure of Mr. Cruz from
Jan to June? Note: Use ‘weighted.mean(liter,
purchase)‘. Write the R scripts and its output.
```{r}
average <- weighted.mean(php, liters)
average
```

