---
title: "RWorksheet_Basa#3b"
author: "Jared J Basa"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a data frame using the table below.

a. Write the codes.
```{r}
Table <- data.frame(
  Respondents = c(1:20),
  Sex = c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2, 2, 1,2),
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1),
  Persons_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_School = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Type_of_House = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)

Table
```
b. Describe the data. Get the structure or the summary of the data
```{r}
str(Table)
summary(Table)
```
c. Is the mean number of siblings attending is 5?
```{r}
meanSiblings_at_School <- mean(Table$Siblings_at_School)
meanSiblings_at_School
```
no 


d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.
```{r}
subsetRespondents <- subset(Table, Respondents <= 2)
subsetRespondents
```
e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
```{r}
rowCols <- Table[c(3, 5), c("Sex", "Persons_at_Home")]
rowCols
```

f. Select the variable types of houses then store the vector that results as types_houses.
Write the codes.
```{r}
Type_of_House <- Table$Type_of_House
Type_of_House
```
g. Select only all Males respondent that their father occupation was farmer. Write the
codes and its output.
```{r}

```

